Spin canonical divisors of log stacky curves

### 2015-06-30 stacky_write_up/spin_cring.tex
new abstract, add Weil divisor to rem, add to bib

\begin{abstract}
  Generalizing the classical theorems of Max Noether and Karl 
	Petri, we describe generators and relations for the spin canonical
	ring of a stacky curve equipped with an arbitrary log divisor. As
	an application, we bound the generation degrees and relation
	degrees for graded rings of modular forms of arbitrary integral
	weight arising from finite-area quotients of the upper half-
	plane by Fuchsian groups.
\end{abstract}

@@

\todo{Peter: I don't like the first thing our reader will read to be a dependent clause}
\todo{Comprehensive change: make sure $\subset$ and $\subseteq$ notation is standardized throughout paper}

@@

We can now consider the orbifold $\Gamma \backslash \BH$ over $\BC$.
For example, in the case $\Gamma$ acts freely on $\BH$, $\Gamma
\backslash \BH$ is a Riemann Surface over $\BC$. It may well be
that $\Gamma \backslash \BH$ is not compact, but we can form a
space $\Gamma \backslash \BH^*$ which is a compactification of
$\Gamma \backslash \BH,$ with associated divisor of cusps $\Delta$.
In order to find generators and relations for $M(\Gamma)$, we
translate the seemingly analytic question of understanding the ring
of modular forms into the algebraic category, using a
generalization of the GAGA principle. By \cite[Proposition 6.1.5]
{vzb:stacky}, there is an equivalence of categories between orbifold
curves and log stacky curves over $\BC$. Hence, for the remainder
of the paper, we will work in the algebraic category.
\todo{mention that we will use the language of Weil divisors?}

@@

\begin{rem}
\label{rem:stack-formalism}
As is done in Voight and Zureick-Brown \cite{vzb:stacky} stacky
curves may be formalized as stacks, but for the purposes of this
paper, it suffices to treat $\sx$ as a scheme whose associated
divisor group allows a finite number of stacky points.
\end{rem}

>>>>

\begin{abstract}
  The study of rings of modular forms arising from finite-area
	quotients of the upper-half plane by Fuchsian groups may be
	translated to the study of canonical rings by the classical
	results of Kodaira--Spencer. In particular, this work describes
	generators and relations of spin canonical rings of a stacky
	curve equipped with an arbitrary log (or effective)	divisor in a
	generalization of the classical theorems of Max Noether	and Karl
	Petri. As an application, these results strongly bound the
	generator and relation degrees for the aforementioned rings
	of modular forms of arbitrary integral weight with some insight
	into rings of modular forms of fractional weight.
\end{abstract}

@@

@@

We can now consider the orbifold $\Gamma \backslash \BH$ over $\BC$.
For example, in the case $\Gamma$ acts freely on $\BH$, $\Gamma
\backslash \BH$ is a Riemann Surface over $\BC$. It may well be
that $\Gamma \backslash \BH$ is not compact, but we can form a
space $\Gamma \backslash \BH^*$ which is a compactification of
$\Gamma \backslash \BH,$ with associated divisor of cusps $\Delta$.
In order to find generators and relations for $M(\Gamma)$, we
translate the seemingly analytic question of understanding the ring
of modular forms into the algebraic category, using a
generalization of the GAGA principle. By \cite[Proposition 6.1.5]
{vzb:stacky}, there is an equivalence of categories between orbifold
curves and log stacky curves over $\BC$. Hence, for the remainder
of the paper, we will work in the algebraic category.

@@

\begin{rem}
\label{rem:stack-formalism}
Stacky curves may be formalized in the language of stacks (e.g. as
done in the works of Voight and Zureick-Brown \cite{vzb:stacky},
Abramovich and Vistoli \cite{abramovich-vistoli:compactifying}, and
Behrend and Noohi \cite{behrend-noohi:uniformization}), but for the
purposes of this paper, it suffices to treat $\sx$ as a scheme
whose associated divisor group allows a finite number of stacky
points. The remainder of the paper will primarily use the language
of Weil divisors.
\end{rem}
